%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Matthew Carullo} \\ \vspace{1pt}
    \small 123-456-7890 $|$ \href{mailto:x@x.com}{\underline{mcarullo@uwaterloo.ca}} $|$ 
    \href{https://linkedin.com/in/...}{\underline{https://www.linkedin.com/in/matthew-carullo/}} $|$
    % \href{https://github.com/...}{\underline{github.com/jake}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Waterloo}{Waterloo, ON}
      {Bachelor of Applied Science in Mechanical Engineering}{Sept. 2019 -- May 2024}
      \resumeItemListStart
        \resumeItem{Academics: 4.0 GPA, Dean's Honors List}
  \resumeSubHeadingListEnd

%-----------SKILLS SUMMARY-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, C/C++, SQL (Postgres), JavaScript, HTML/CSS, R} \\
     \textbf{Frameworks}{: React, Node.js, Flask, JUnit, WordPress, Material-UI, FastAPI} \\
     \textbf{Developer Tools}{: Git, Docker, TravisCI, Google Cloud Platform, VS Code, Visual Studio, PyCharm, IntelliJ, Eclipse} \\
     \textbf{Libraries}{: pandas, NumPy, Matplotlib}
    }}
 \end{itemize}



%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Engineering Analyst}{Aug. 2024 -- Present}
      {Hatch Ltd.}{mississauga, ON}
      \resumeItemListStart
        \resumeItem{Developed a software platform for acoustic and ultrasonic signal processing from NDT inspections,
          reducing analysis time by 40\% and improving defect detection accuracy by 30\%.}
        \resumeItem{Designed, implemented, and documented process work instructions and technical reports to support
          multi-million-dollar maintenance and reline decisions.}
        \resumeItem{Analyzed large-scale time-frequency process data to identify efficiency improvements, driving
          measurable reductions in downtime and operational costs.}
        \resumeItem{Managed end-to-end execution of 20+ industrial inspection campaigns across global sites, ensuring
          on-time delivery under challenging plant conditions.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Mechanical Design Engineer}{May. 2023 -- Aug. 2023}
      {Tesla Toronto Automation}{Markham, ON}
      \resumeItemListStart
        \resumeItem{Designed and implemented upgraded powertrain systems for high-speed automated lithium-ion cell
          assembly machinery to enhance precision and reliability.}
        \resumeItem{Led tooling and fixture modifications for mechanical sealing systems, conducting statistical quality
          control studies to validate performance.}
        \resumeItem{Collaborated cross-functionally to integrate equipment upgrades into existing manufacturing lines,
          minimizing downtime during transition.}
    \resumeItemListEnd

    \resumeSubheading
      {Product Design Engineer}{Sept. 2022 -- Dec. 2022}
      {Tesla Inc.}{Palo Alto, CA}
      \resumeItemListStart
        \resumeItem{Designed 3D-printable tooling components to safeguard critical Semi-truck electronics, preventing
          potential \$25M+ in damage during product launch.}
        \resumeItem{Reviewed new process/equipment designs for manufacturability and robustness, working closely with
          mechanical development teams to ensure seamless transition to production.}
        \resumeItem{Created assembly tools and fixtures for supercomputer cabinet manufacturing, improving production
          ergonomics and throughput.}
      \resumeItemListEnd

    \resumeSubheading
      {Process Optimization Engineer}{Jan. 2022 -- Apr. 2022}
      {Tesla Inc.}{Fremont, CA}
      \resumeItemListStart
        \resumeItem{Spearheaded process validation and optimization of laser welding systems, improving yield from 92\%
          to 99.8\% through structured data analysis and equipment tuning.}
        \resumeItem{Developed and implemented enhanced vision system leveraging machine learning to improve defect
          detection in lithium-ion cell welds.}
        \resumeItem{Coordinated with operations and quality teams to introduce off-line inspection points and SOPs,
          increasing product quality while reducing rework.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd





%-------------------------------------------
\end{document}
